---
title: "data product2"
author: "sakinah"
date: "April 4, 2016"
output: ioslides_presentation
---

## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

### Developing Data Products

- Course Project

- Application for the best car to buy 

- by Sakinah


## Introduction
This presentation is part of the Course Project for the Coursera Developing Data Products class. The peer assessed assignment has two parts. First, we need to create a Shiny application and deploy it on Rstudio's servers. Second, we should use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about the application. This presentation adresses the second part of the course project.

The app developed for the first part of the assignment is avalilable at:

https://sssa79.shinyapps.io/shinyapps/

Source code for ui.R and server.R files are available on the GitHub:

https://github.com/sakinahUTEM/Shiny-Application

```{r}
summary(cars)
```

## Slide with Plot

```{r, echo=FALSE}
plot(cars)
```

